Supporting Information

### 2018-03-30 SupportingInformation.Rmd
finished editing through the aphid ff results

<!--Shya, can you please organize these following plots into one plot with mutliple panels?-->
![Plot for aphid-count : Spearman vs. Distance\label{fig_count_spear}](./Results/stat_results/stat_aphid_count/Sp_10_Spearman_vs_D.pdf){ width=50%, height=50% }

@@

```{r stat_aphid_ff, echo=F, cache=T, cache.extra=list(seed,data_aphid_ff,mtime("NonParamStat.R"))}
set.seed(seed)
resloc<-"./Results/stat_results/stat_aphid_ff/"

@@

```{r tab_ff_resamp,echo=F,results="markup"}
s<-stat_aphid_ff$numericdf[,2:5]
rownames(s)<-c("spear","kend","cor~l~","cor~u~","P~l~","P~u~","$D^2$~l~","$D^2$~u~","cor~l~ - cor~u~","P~l~ - P~u~","$D^2$~u~ - $D^2$~l~")
knitr::kable(s,
             format = "pandoc",
             caption = "Aphid_firstflight : resampling result for stat indicating upper tail dependence\\label{tab_ff_resamp}",
             booktabs=TRUE)
```

![copula plot for aphid-firstflight\label{fig_ff_allcop}](./Results/stat_results/stat_aphid_ff/Sp_11_AllCops.pdf)

![Plot for aphid-firstflight : Spearman vs. Distance\label{fig_ff_spear}](./Results/stat_results/stat_aphid_ff/Sp_11_Spearman_vs_D.pdf){ width=50%, height=50% }

@@

Table \ref{tab_ff_resamp} shows the mean of each non-parametric statistic taken from all pairwise locations and then based on a resampling results how the resampled mean distributed from or around the real mean. Fourth column named $fracgt0$ in Table \ref{tab_ff_resamp} indicates the fraction of resampled mean greater then zero. $\cor_l-\cor_u$, $\Ps_l-\Ps_u$ and $\Dsq_u-\Dsq_l$ statistic with negative mean has all resampled mean less than $0$ for *Leaf-curling plum aphid*-firstflight data. This proves that there is a significant upper tail dependence in *Leaf-curling plum aphid*-firstflight data.

>>>>

<!--Shya, can you please organize these following plots into one plot with mutliple panels? Once that is done, please add some text describing these results.-->
![Plot for aphid-count : Spearman vs. Distance\label{fig_count_spear}](./Results/stat_results/stat_aphid_count/Sp_10_Spearman_vs_D.pdf){ width=50%, height=50% }

@@

<!--Do the analysis-->
```{r stat_aphid_ff, echo=F, cache=T, cache.extra=list(seed,data_aphid_ff,mtime("NonParamStat.R"))}
set.seed(seed)
resloc<-"./Results/stat_results/stat_aphid_ff/"

@@

Mean values of our statistics ($\cor_l$, $\cor_u$, $\Ps_l$, $\Ps_u$, $\Dsq_l$, $\Dsq_u$, 
$\cor_l-\cor_u$, $\Ps_l-\Ps_u$, $\Dsq_u-\Dsq_l$), as well as mean Kendall and Spearman 
correlations, were 
computed across all pairs of sampling locations, and confidence intervals of these means were 
computed via a spatial
resampling scheme, as described in Methods (Table \ref{tab_count_resamp}).
Confidence intervals of
$\cor_l$, $\cor_u$, $\Ps_l$, $\Ps_u$, $\Dsq_l$, and $\Dsq_u$ always excluded 
zero and mean values were positive,
indicating tail dependence.
Confidence intervals of $\cor_l-\cor_u$, $\Ps_l-\Ps_u$, $\Dsq_u-\Dsq_l$ also always 
exluded $0$ and were negative, indicating asymmetry of tail dependence, a feature 
that data with normal copula 
structure do not have, providing further evidence answering the third part of question 1.
The contrast here with the analogous results for abundances of the green spruce aphid is 
again illuminating.

<!--display the main statistical results in a table-->
```{r tab_ff_resamp,echo=F,results="markup"}
s<-stat_aphid_ff$numericdf[,c(3,2,4)]
colnames(s)<-c("Lower 95\\% CI", "Mean", "Upper 95\\% CI")
rownames(s)<-c("Spearman","Kendall","$\\cor_l$","$\\cor_u$","$\\Ps_l$","$\\Ps_u$","$\\Dsq_l$","$\\Dsq_u$","$\\cor_l - \\cor_u$","$\\Ps_l - \\Ps_u$","$\\Dsq_u - \\Dsq_l$")
knitr::kable(s,
             format = "pandoc",
             caption = "Spatially averaged values of statistics and confidence intervals based on resampling for first flight data for the leaf-curling plum aphid.\\label{tab_ff_resamp}",
             booktabs=TRUE)
```

<!--As for the count data, I don't think we need this. If you disagree, let me know, otherwise pls delete the commented text and this comment.
![copula plot for aphid-firstflight\label{fig_ff_allcop}](./Results/stat_results/stat_aphid_ff/Sp_11_AllCops.pdf)
-->

<!--Shya, can you please organize these following plots into one plot with mutliple panels? Once that is done, please add some text describing these results.-->
![Plot for aphid-firstflight : Spearman vs. Distance\label{fig_ff_spear}](./Results/stat_results/stat_aphid_ff/Sp_11_Spearman_vs_D.pdf){ width=50%, height=50% }

@@

<!--Dan stopped editing here 2018 03 30-->
